### 2016-01-25 sections/data0.0.tex
Adding first bit of M101 data

\section{DATA}
Our sample contains photometric and spectroscopic data of M31 and M101, as well as their measured properties such as SFR, stellar mass, dust luminosity, metallicity, and gas mass.    
%M31 data: observed ones;
    \subsection{M31 data}
     Our M31 data sample contains data from ten regions from outer part of the disk . Data for PAH are for M31 spectroscopy data for our 10 regions came from observations using {\it Spitzer}/Infrared Spectrograph \citep{Dim15}. \cite{Dim15}

%M31 data: measured ones;
%M101 data: observed ones;

>>>>

\section{DATA}

%Our sample contains photometric and spectroscopic data of M31 and M101, as well as their measured properties such as SFR, stellar mass, dust luminosity, metallicity, and gas mass.    
For creating SOM, we used spectroscopy and photometry data as well as their measured properties such as SFR, stellar mass, dust luminosity and mass, metallicity, and gas mass from 10 regions in M31 (Fig~\ref{fig: region in m31}) and 8 regions in M101 (Fig~\ref{fig: region in m101}).
Table~\ref{tab: data} shows list of the sample and their unit for both M31 and M101.
%M31 data 
%%%%% Sahar: More detail?
    \subsection{M31 data}

     The 10 regions in M31 were chosen due to availability of the PAH data for them. 
     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/Infrared Spectrograph\citep[IRS,][]{Houck04b} observations. 
     They used {\tiny PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
     For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
     We used radiation hardness index instead of flux of individual atomic line, since they were only calculate the upper limit flux for most of the lines in most of the regions.

     For photometry part of the sample, we used data from \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [SII] continuum and [OIII} continuum emission~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12}.
     We changed units of all our data to Wm$^{-2}$ to be the same unit as PAH fluxes.
     We used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Chemin09}.
     We also utilized SFR(FUV + 24$\mu$m), stellar mass, total gas mass data from \cite{Rahmani16}, and dust luminosity and mass data from \cite{Draine14}.

%M101 data: observed ones;
    \subsection{M101 data}
     For M101 galaxy, we used PAH fluxes which had been measured using {\tiny PAHFIT IDL} tool and reported in \cite{Gordon08}. 
     We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101. 
     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS24 and 70~$\mu$m~\cite{Dale09}, and  PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\cite{Kennicutt11}.

### 2016-01-25 sections/method0.0.tex
Adding first bit of M101 data

     Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$ and we want to map them on S1 by S2 map. 
     We start by creating S1 $\times$ S2 empty neurons. 
     The initial arrangement of these neurons depends on a map's topology provided by user.
     Since the topology of the map does not have any affect on the final result, we chose hexagonal topology which is the default topology for SOMs.
     Then, we assign a random weight vector \boldit{W} $\in \Re^n$ to each node.
     The process of creating SOM, happens over series of $N$ iterations. 
     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
     We test our code by varying the number of iterations and find $N = 100$ is optimized for our sample. For each iteration:
     \begin{enumerate}
     \item Choose a random vector from our data set.
     \item Calculate the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and find a neuron with ``$D_{j_{min}}$". This neuron is the winner node and is calling Best Matching Unit (BMU). 
     \item  Compute the radius of the neighbourhood of the BMU to find nodes within this radius. The weight vectors of these nodes will be affected in the next steps. This value is arbitrary but initially can be chosen to be half of the size of the SOM and then it decades exponentially over each iteration:
   \begin{equation}
   r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
   \end{equation}
   where $\tau$ is a decay constant and usually set to be the same as number of iterations, $N$. $r^0_{BMU}$ and $r^t_{BMU}$ is the radius of the neighbourhood at 0th and $t$th iteration, respectively. 
   \item Change the weight vectors of the BMU and all the nodes within r(t) as:
   \begin{equation}
   \label{equ: weight adj}
   w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
   \end{equation}
   where $L(t) = e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate. $R(t)$ determines how weight of nodes in the neighbourhood of BMU will change.
   \item  Repeat these steps for $N$ times.
    \end{enumerate}

    In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep{sommatlab}. 
    In Section~\ref{sec: test model} we used this toolbox to create SOMs from SED of galaxies and learn how this method works and how we can interpret the results.

>>>>

     Assuming we have a data set which contains vectors, \boldit{V} $\in \Re^n$ and we want to map them on S1 by S2 map. 
     We start by creating S1 $\times$ S2 empty neurons. 
     The initial arrangement of these neurons depends on a map's topology provided by user.
     Since the topology of the map does not have any affect on the final result, we chose hexagonal topology which is the default topology for SOMs.
     Then, we assign a random weight vector \boldit{W} $\in \Re^n$ to each node.
     The process of creating SOM, happens over series of $N$ iterations. 
     During each iteration the weight vectors might change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
      In each iteration:
     \begin{enumerate}
     \item Choose a random vector from our data set.
     \item Calculate the euclidean distance for each node j as  $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and find a neuron with ``$D_{j_{min}}$". This neuron is the winner node and is calling Best Matching Unit (BMU). 
     \item  Compute the radius of the neighbourhood of the BMU to find nodes within this radius. The weight vectors of these nodes will be affected in the next steps. This value is arbitrary and initially can be set to be as high as half of the SOM size and then it decades exponentially over each iteration:
   \begin{equation}
   r^t_{BMU} = r^0_{BMU}e^{(-t/\tau)}
   \end{equation}
   where $\tau$ is a decay constant and usually set to be the same as number of iterations, $N$. $r^0_{BMU}$ and $r^t_{BMU}$ is the radius of the neighbourhood at 0th and $t$th iteration, respectively. 
   \item Change the weight vectors of the BMU and all the nodes within r(t) as:
   \begin{equation}
   \label{equ: weight adj}
   w(t+1)=w(t)+L(t) \times R(t) \times(v(t)-w(t))
   \end{equation}
   where $L(t) = e^{(-t/\tau)}$ is the learning factor which prevents divergence of the SOM and $R(t)=exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate. $R(t)$ determines how weight of nodes in the neighbourhood of BMU will change.
   \item  Repeat these steps for $N$ times.
    \end{enumerate}

    In order to create SOM, we used {\tiny MATLAB} neural network toolbox~\citep{sommatlab}. 
    We created different SOM with different sizes, initial neighbourhood, and iteration numbers to find the optimize result for our sample.
    We test our code by varying the number of iterations and find $N = 100$ is optimized for our sample.
    In Section~\ref{sec: test model} we used this toolbox to create SOMs from SED of galaxies and learn how this method works and how we can interpret the results.
